Price of Anarchy for Mean Field Games

### 2018-07-23 PoA.tex
update prop 6 second half

	Hence, from inequalities (\ref{eq:I_1_b2_bar_infinity}) and (\ref{eq:I_2_b2_bar_infinity}), for all $\bar{b}_2 \geq \bar{b}_2^* := \max \{ \bar{b}_2^{*,I_1}, \bar{b}_2^{*,I_2}\}$ we have:
	\begin{equation*}
		\Delta SC = I_1 + I_2 \leq 2\epsilon.
	\end{equation*} 
	Therefore, by taking $\epsilon \to 0$, we obtain:
	\begin{equation*}
		\lim_{\bar{b}_2 \to \infty} \Delta SC = 0.
	\end{equation*}

>>>>

	Hence, from inequalities (\ref{eq:I_1_b2_bar_infinity}) and (\ref{eq:I_2_b2_bar_infinity}), for all $\bar{b}_2 \geq \bar{b}_2^* := \max \{ \bar{b}_2^{*,I_1}, \bar{b}_2^{*,I_2}\}$ we have:
	\begin{equation*}
		\Delta SC = I_1 + I_2 \leq 2\epsilon.
	\end{equation*} 
	Therefore, we can set $\epsilon_1, \epsilon_2,\epsilon_3$ as the following constants:
	$$ \epsilon_1 := \frac{1}{2} \min \left\{c_{\delta_u^{\bar{b}_2 \to \infty}}, c_{\delta_w^{\bar{b}_2 \to \infty}} \right\}, \quad  \epsilon_2 := \frac{c_u}{2}, \quad \epsilon_3 = \frac{m_u(\epsilon_1)}{2},$$ and following the previous analysis by taking $\epsilon \to 0$, we obtain:
	\begin{equation*}
		\lim_{\bar{b}_2 \to \infty} \Delta SC = 0.
	\end{equation*}
